---
title: "reportRx TestFile"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
  bookdown::word_document2:
    reference_docx: 'wordTemplate.docx'
    toc: yes
sansfont: Calibri Light
mainfont: Calibri Light
bibliography:
  - bibfile.bib
#csl: Vancouver.csl
link-citations: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#library(reportRx)
library(tidyverse)
devtools::load_all()
```


\newpage
# Introduction {-}

Citations can be made like this for R packages [@R-reportRx], or [@R-base] for the R language itself. Other citations must match those found in your master bibfile. 

First, make some changes to the lung data (cancer in the newer version of survival)

```{r echo=T}
data(cancer, package='survival')
lung <- cancer

lung <- lung %>%
  mutate(
    Status=factor(status-1),
    Sex = factor(sex,labels = c('Male','Female')),
    AgeGroup = cut(age, breaks=seq(0,100,10)),
    OneLevelFactor = factor(x='one level')
  ) %>%
  arrange(Status)

lung$x_null = rnorm(nrow(lung))
lung$x_pred = c(rnorm(sum(lung$Status==0),0,1),
                rnorm(sum(lung$Status==1),1,1))
set.seed(1)
test_data = tibble(
  y= rnorm(1000),
  x0= geoR::rboxcox(1000, lambda=.5, mean=10, sd=2),
  x1= x0+y
)
```

# Numbered Heading

## Test covsum

```{r test-covsum-1}
rm_covsum(data=lung,
          covs=c('Status','Sex','age','AgeGroup','meal.cal','OneLevelFactor'),
          caption='Test Special characters in caption 80% $100.')

```

```{r test-covsum-2}
rm_covsum(data=lung,
          covs=c('Status','age','AgeGroup','meal.cal','OneLevelFactor'),
          maincov = 'Sex')
```

\newpage

Make sure it still works when there are empty levels

In a covariate:

```{r test-covsum-3}

test_empty <- lung
test_empty$AgeGroup[test_empty$Sex=='Female'] <- NA

rm_covsum(data=test_empty,
          covs=c('Status','age','AgeGroup','meal.cal','OneLevelFactor'),
          maincov = 'Sex')
```

In the main covariate:

```{r test-covsum-4}

test_empty <- lung
test_empty$Sex[test_empty$Sex=='Female'] <- NA

rm_covsum(data=test_empty,
          covs=c('Status','age','AgeGroup','meal.cal','OneLevelFactor'),
          maincov = 'Sex')

```

\newpage

The chi-square is the default setting, unless there are low counts, check that this works properly
This should have two Chi-Sq tests:

```{r}

rm_covsum(data=test_empty,
          covs=c('AgeGroup','Status'),
          maincov = 'Sex',
          testcat='Chi-squared',
          show.tests=T)

```

Here age group should be analysed with a Fisher test:

```{r}

rm_covsum(data=test_empty,
          covs=c('AgeGroup','Status'),
          maincov = 'Sex',
          show.tests=T)

```

\newpage

If you need to run an `rm_` function in a loop, you need to use the following syntax. Unfortunately, this produces a NULL after each table when you knit to Word. This can be prevented by removing the `print` function wrapped around the `rm_covsum` call, but then nothing will print if you knit to pdf .... So, if you are going to flip back and forth, leave the print command and do a find and replace on the resulting NULL words in the Word document. 

```{r results='asis',echo=T}

pander::panderOptions('knitr.auto.asis', FALSE)

for (v in names(lung)[1:2]){
  cat("\n")
  print(rm_covsum(data=lung,covs=v))
  cat("\n")
}

pander::panderOptions('knitr.auto.asis', TRUE)
```

\newpage

## Test plotuv

Figure \@ref(fig:test-plotuv) shows the bivariate relationships between the response and covariates. Figure referencing works only when a figure caption is provided in the chunk options. Note that underscores and not allowed in the chunk names, only hyphens.

```{r test-plotuv, fig.cap= 'Associations between status and covariates in the lung data.'}
plotuv(data=lung,
       covs=c('Sex','age','AgeGroup','meal.cal','OneLevelFactor'),
       response = 'Status',
       response_title = 'Test Response Title',
       showN=T
)
```



```{r test-plotuv-2, fig.cap= 'Associations between status and covariates in the lung data.'}
plotuv(data=lung,
       covs=c('Sex','Status','AgeGroup','meal.cal','OneLevelFactor'),
       response = 'age',
       showN=T
)
```

## Tests for uvsum

### Test logistic

Tables \@ref(tab:test-uv-logistic-1), \@ref(tab:test-uv-logistic-2) and \@ref(tab:test-uv-logistic-3) display the logistic regression results with different confidence interval widths. If the document in knit to pdf, the chank-lable option will not be used, instead the name of the chunk will be used in cross-referening. For Word tables the chunk label needs to be added into the function call.

```{r test-uv-logistic-1}
rm_uvsum(response = 'Status',
         covs=c('age','Sex','wt.loss'),
         data=lung,
         digits=3,
         type='logistic',
         chunk_label = 'test-uv-logistic-1' )


```

```{r test-uv-logistic-2}
rm_uvsum(response = 'Status',
         covs=c('age'),
         data=lung,
         type='logistic',
         CIwidth=.9,
         chunk_label='test-uv-logistic-2')
```

```{r test-uv-logistic-3}
rm_uvsum(response = 'Status',
         covs=c('age'),
         data=lung,
         type='logistic',
         CIwidth=.99,
         chunk_label='test-uv-logistic-3')

```

### Test Linear
```{r test-uv-linear}
rm_uvsum(response = 'wt.loss',
         covs=c('Status','Sex','ph.ecog','meal.cal','age'),
         data=lung,
         CIwidth=.95)
# rm_uvsum(response = 'wt.loss',
#          covs=c('age'),
#          data=lung,
#          CIwidth=.90)

```

### Test coxph 
```{r test-uv-coxph}
rm_uvsum(response = c('time','status'),
         covs=c('Sex','ph.ecog','meal.cal','age'),
         data=lung,
         CIwidth=.99)

```

### Test crr 
See Appendix

### Test ordinal

```{r test-uv-ord}
mtcars$cyl <- factor(mtcars$cyl,ordered=T)
rm_uvsum(response = 'cyl',
         covs=c('qsec'),
         data=mtcars,
         CIwidth=.90)


```

### Test crr
```{r test-uv-crr}
rm_uvsum(response = c('time','status'),
         covs=c('Sex','ph.ecog','meal.cal','age'),
         data=lung,
         type='crr',
         CIwidth=.90)

rm_uvsum(response = c('time','status'),
         covs=c('age'),
         data=lung,
         type='crr')

```

### Test boxcox
```{r test-uv-boxcox}
rm_uvsum(response = 'y',
         covs=c('x0','x1'),
         data=test_data,
         type='boxcox',
         CIwidth=.90)
```

### Test  geeglm 

```{r}
data(BodyWeight,package='nlme')


rm_uvsum(response = 'weight',
         covs=c('Time','Diet'),
         id='Rat',
         corstr="ar1",
         family=gaussian("identity"),
         data=BodyWeight,showN=T)

```

\newpage

# KM plit with confidence intervals
```{r}
ggkmcif(response = c('time','status'),data=lung,median.text = T,set.time.text = 'Y OS',
        set.time = c(500,100,1100),conf.type = 'log-log',conf.curves=TRUE)

```

## modify a KM plot 

```{r}
km <- ggkmcif(response = c('time','status'),data=lung,median.text = T,set.time.text = 'Y OS',
              set.time = c(500,100,1100),conf.type = 'log-log',conf.curves=TRUE,returns = T)
km[[1]] <- km[[1]] + ggplot2::theme_minimal()
modify_ggkmcif(km)
```


\newpage

# Unnumbered Heading {-}

## Test etsum

To get nice output from  `rm_etsum` you must set `results='asis' in the chunk options`

otherwise you get this:

```{r, eval=T}
rm_etsum(data = lung, response = c("time","status"), group = 1,
         times=c(365,720,1095), units="days")

```

when you want this:

```{r, results='asis'}
rm_etsum(lung,c("time","status"),"Sex",c(1,2,3),"months")
```

## Test mvsum 


Comments from Susie 8 Oct
```{r}
library(survival)
data <- read.csv('../reportRxTestData/sampledata.csv')
str(data)

table(data$Chemo_Yes_No)
class(data$Chemo_Yes_No)
table(data$RT_QA)
class(data$RT_QA)

m1 <- coxph(Surv(OStime,OS)~ RT_QA + Chemo_Yes_No,  data)
rm_mvsum(model=m1,data=data)

response <- names(m1$model)[1]

```



### Test with glm

```{r}
m = glm(Status~wt.loss+Sex+AgeGroup,
        data=lung,
        family='binomial')
rm_mvsum(model=m,data = lung,p.adjust='holm',showN=T)
rm_mvsum(model=m,p.adjust='holm',showN=T)

fit_lm = lm(wt.loss~age+Sex,data=lung)
rm_mvsum(model=fit_lm,showN=T)

```

```{r}
## Dobson (1990) Page 93: Randomized Controlled Trial :
counts <- c(18,17,15,20,10,20,25,13,12)
outcome <- gl(3,1,9)
treatment <- gl(3,3)
pois_data <- data.frame(treatment, outcome, counts) # showing data
glm.D93 <- glm(counts ~ outcome + treatment, data=pois_data, family = poisson())
rm_mvsum(model=glm.D93,data = pois_data)
```

### Test with glm, linear

```{r}
m = glm(wt.loss~Sex+age,
        data=lung,
        family='gaussian')
#summary(m)
rm_mvsum(model=m,data = lung)
```

### Test with lm

```{r}
m = lm(wt.loss~Status+Sex+age,
       data=lung)
rm_mvsum(model=m,data = lung,p.adjust='hochberg')

```

### Test with lme

```{r}

library(nlme)
data(BodyWeight)
fm1BW.lme <- lme(weight ~ Time * Diet, BodyWeight,random = ~ Time)
#summary(fm1BW.lme)
rm_mvsum(model=fm1BW.lme,data=BodyWeight)
rm_mvsum(fm1BW.lme,showN = T)




```

### Test with polr


```{r}
library(MASS)
data(housing)
options(contrasts = c("contr.treatment", "contr.poly"))
house.plr <- MASS::polr(Sat ~ Infl + Type + Cont, weights = Freq, data = housing)
#summary(house.plr)
rm_mvsum(model=house.plr)
rm_mvsum(model=house.plr,showN=T)


```

### Test crr
```{r}
# From the crr help file
set.seed(10)
ftime <- rexp(200)
fstatus <- sample(0:2,200,replace=TRUE)
cov <- matrix(runif(600),nrow=200)
dimnames(cov)[[2]] <- c('x1','x2','x3')
df <- data.frame(ftime,fstatus,cov)
m1 <- crrRx(as.formula('ftime+fstatus~x1+x2+x3'),df)

# summary(m1)
rm_mvsum(m1,data=df,showN = T)
# rm_mvsum(m1,data=df,showN = F)

# df2 <- df
# df2[sample(1:nrow(df),5),3] <- NA
# df2[sample(1:nrow(df),5),4] <- NA
# df2[sample(1:nrow(df),5),5] <- NA
# 
# m2 <- crrRx(as.formula('ftime+fstatus~x1+x2+x3'),df2)
# #rm_mvsum(model=m2,showN = T) # data must be supplied for crr models
# rm_mvsum(m2,data=df2,showN = T) # good
# #rm_mvsum(m2,data=df,showN = T) # This is wrong, because the data supplied is wrong
# 
# df3 <- na.omit(df2)
# m3 <- crrRx(as.formula('ftime+fstatus~x1+x2+x3'),df3)
# rm_mvsum(m3,data=df3,showN = T) # This is right
# 

```

### Test  geeglm 

```{r}
library(geepack)
data(BodyWeight,package='nlme')
fm1BW.lme <- lme(weight ~ Time * Diet, BodyWeight,random = ~ Time)

gee1 <- geeglm(weight ~ Time+Diet , data=BodyWeight, id=Rat, family=gaussian("identity"), corstr="ar1")
summary(gee1)
rm_mvsum(gee1,data=BodyWeight,showN=T)

```

## TO DO fix- bug
```{r, eval=F,echo=T}
library(geepack)
data(dietox)
dietox$Cu     <- as.factor(dietox$Cu)
mf <- formula(Weight ~ Cu * (Time + I(Time^2) + I(Time^3)))
gee1 <- geeglm(mf, data=dietox, id=Pig, family=poisson("identity"), corstr="ar1")
summary(gee1)
mvsum(gee1,data=dietox)

```


\newpage

## Test forestplot2
```{r}
forestplot2(house.plr)
```

\newpage

## Combining uvsum and mvsum tables

Linear models

```{r}
uvsumTable  <- rm_uvsum(response = 'wt.loss',
         covs=c('Status','Sex','ph.ecog','meal.cal','AgeGroup'),
         data=lung,
         CIwidth=.95,
         tableOnly = T)

m <- lm(wt.loss~Status+Sex+ph.ecog+meal.cal+AgeGroup,data=lung)
mvsumTable  <- rm_mvsum(m, tableOnly = T,showN=T)

rm_uv_mv(uvsumTable,mvsumTable)
```


Logistic models

```{r}
uvsumTable  <- rm_uvsum(response = 'Status',
         covs=c('Sex','ph.ecog','meal.cal','AgeGroup'),
         data=lung,
         CIwidth=.95,
         tableOnly = T)

m <- glm(Status~Sex+ph.ecog+meal.cal,data=lung,family='binomial')
mvsumTable  <- rm_mvsum(m, tableOnly = T,showN=T)

rm_uv_mv(uvsumTable,mvsumTable)
```

\newpage

## Combining Tables with nestTable

```{r}
m1 = glm(Status~wt.loss+Sex,
         data=lung,
         family='binomial')
tab1 <- rm_mvsum(model=m1,data = lung,p.adjust='none',tableOnly = T,showN=T)
m2 = glm(Status~wt.loss+Sex+AgeGroup,
         data=lung,
         family='binomial')
tab2 <- rm_mvsum(model=m2,data = lung,p.adjust='none',tableOnly = T,showN = T)

tab1$Model = 'Model 1'
tab1$`p-value` = NA # necessary to make the columns match
tab2$Model = 'Model 2'

newtab <- rbind(tab1,tab2)
nestTable(data=newtab[,c(5,1,2,6,3,4)],
          head_col = 'Model',to_col = 'Covariate')



```

Check - what happens if the columns aren't sorted?
```{r}

newtab <- rbind(tab1,tab2)
newtab <- newtab[c(1,2,6:8,4:5,9:15),]
nestTable(data=newtab[,c(5,1,2,6,3,4)],
          head_col = 'Model',to_col = 'Covariate')

```

\newpage

# covsum and missing values

Add some more examples here...

No Missing Values
```{r}
data("mtcars")
mtcars$Cylinders <- as.factor(mtcars$cyl)
mtcars$Transmission <- factor(mtcars$am,levels=0:1,labels=c('Automatic','Manual'))
rm_covsum(data=mtcars,
          maincov = 'Transmission',
          covs=c('mpg','Cylinders','qsec'),show.tests=T)

```

Adding in some extra rows with missing values on Cylinders and mpg

```{r}

missingData <- data.frame(Transmission = rep(c("Automatic","Manual"),each=10),Cylinders=NA,mpg=NA,qsec=NA)
mtcars2 <- bind_rows(mtcars,missingData)
rm_covsum(data=mtcars2,
          maincov = 'Transmission',
          covs=c('mpg','Cylinders','qsec'),show.tests=T)

```


```{r, eval=F}
# ReportRx Code Dependencies
exportedFunctions <- ls("package:reportRx")

# get all functions inside the package using asNamespace
all_funs <- unclass(lsf.str(envir = asNamespace("reportRx"), all.names = T))
# get only non exported funs
hiddenFunctions <- setdiff(all_funs, exportedFunctions)

RxFuns <- data.frame(fName = c(exportedFunctions,hiddenFunctions),
                     fStatus = c(rep('Exported',length(exportedFunctions)),
                                 rep('Hidden',length(hiddenFunctions))))

RxFuns %>% write.csv('../reportRxFunctionList.csv')
```

\newpage

# References

<!-- NOTE: This is a comment and will not appear in the final document -->

<div id="refs"></div> <!-- This is only necessary if you need something after the Reference section -->

\newpage

# Appendix

## Comparing p-values

P-values agree between 

```{r}
lung$ECOG <- as.factor(lung$ph.ecog)
rm_uvsum(response = 'wt.loss',
         covs=c('status','Status','sex','Sex','ph.ecog','ECOG'),
         data=lung,
         CIwidth=.95)
```

With lm:

```{r}
l1 <- lm(wt.loss~Sex,data=lung)
summary(l1)

```

With t-test (using the default of non-homogenous variance):

```{r}
t1 <- t.test(wt.loss~Sex,data=lung)
t1
t1$p.value

```


With t-test using the pooled variance:

```{r}
t2 <- t.test(wt.loss~Sex,data=lung,var.equal=T)
t2
t2$p.value

```

